Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-06-04 draft/accordionComplexSurfaces.tex
Changed the definition of dissection.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ crosses a face~$f$ of~$\dissection$,
\begin{itemize}
\item the two edges of~$f$ crossed by~$\alpha$ share a marked point~$v \in M$,
\item the marked points~$v$ and~$f\dual$ lie on opposite sides of~$\alpha$ in~$f$
\end{itemize}
\end{definition}

>>>>

We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
This is always possible up to homotopy. \pierreguy{Reference?}
With this assumption, each segment of a~$B$-arc that lies in a face~$f$ of the dissection~$\dissection$ has two intersection points (called crossings) with the edges of~$f$.
Note that the edges of~$f$ may be on the boundary of the surface.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ crosses a face~$f$ of~$\dissection$,
\begin{itemize}
\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,
\item there exists a marked points~$v$ shared by~$e_1$ and~$e_2$ such that~$v$ and~$f\dual$ lie on opposite sides of~$\alpha$ in~$f$.
\end{itemize}
\end{definition}
